### 2016-12-18 thesis/latex/thesis.tex
Add bibtex stuff.

@@

\subsubsection{Why does the cell need motor transport?}
This ties in a lot to the previous section. I originally thought of putting the <x> vs T diffusion/
motor plot in the introduction, but maybe it would be better here. Not sure.\\

@@

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{/home/elliotc12/dynein_walk/figures/equilibrium-onebound}
  \caption{Definition of equilibrium angles.}
  \label{fig:eq_angles}
\end{figure}

@@

  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{/home/elliotc12/dynein_walk/figures/OB_Average_PE.pdf}
    \caption{Onebound PE vs time.}
  \end{minipage}
  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{/home/elliotc12/dynein_walk/figures/BB_Average_PE.pdf}
    \caption{Bothbound PE vs time.}
  \end{minipage}
  \label{fig:equipartition_agreement}
\end{figure}

@@

Calirimetry could get Gibb's energy of binding if you froze the motor in onebound using
vanadium? Maybe...\\
\subsection{Possible further projects}
\subsection{Difference between dynein and kinesin}
Our project un/successfully predicted how dynein behaved. How would we modify it to describe kinesin?
Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion? This
would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility
and get its crystal structure to do some comparisons.

>>>>

\bibliographystyle{plain}

@@

\subsubsection{Why does the cell need motor transport?}

\cite{dewitt2012cytoplasmic}

This ties in a lot to the previous section. I originally thought of putting the <x> vs T diffusion/
motor plot in the introduction, but maybe it would be better here. Not sure.\\

@@

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{../figures/equilibrium-onebound}
  \caption{Definition of equilibrium angles.}
  \label{fig:eq_angles}
\end{figure}

@@

  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
    \caption{Onebound PE vs time.}
  \end{minipage}
  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
    \caption{Bothbound PE vs time.}
  \end{minipage}
  \label{fig:equipartition_agreement}
\end{figure}

@@

Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using
vanadium? Maybe...\\
\subsection{Possible further projects}
\subsection{Difference between dynein and kinesin}
Our project un/successfully predicted how dynein behaved. How would we modify it to describe kinesin?
Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion? This
would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility
and get its crystal structure to do some comparisons.

\bibliography{thesis}
